---
title: "Exploratory summaries/visualizations"
author: "TJ"
format: pdf
editor: visual
execute:
  echo: false    # Hides all code globally
  warning: false # Suppresses all warnings globally
---

## Description

# This code results some exploratory summaries/visualizations graphs that use to assess the results in pilot survey data

```{r,echo=FALSE, warning=FALSE, message=FALSE}
# Clean the memory
rm(list = ls())  # Removes all objects in the environment

library(readr)
library(dplyr)
library(apollo)
library(ggplot2)
library(officer)
library(flextable)
library(tidyr)
library(haven)
library(here)
library(grid)
library(ggtext)
library(knitr)
```

1.  **Vote count % at different bid levels**

```{r,echo=FALSE, warning=FALSE, message=FALSE}

df <- read_csv(here("Deriveddata", "processed_finaldata_batch_1_Apollo.csv"))


# 1. Vote count % at different bid levels
df1 <- df%>%
  select(COST,VOTE)


df_summary <- df1 %>%
  group_by(COST) %>%
  summarize(
    Percent_1 = sum(VOTE == 1) / n() * 100,
    Percent_0 = sum(VOTE == 0) / n() * 100
  )

df_long <- df_summary %>%
  pivot_longer(cols = starts_with("Percent"), names_to = "Vote", values_to = "Percentage") %>%
  mutate(Vote = ifelse(Vote == "Percent_1", "1", "0"))

ggplot(df_long, aes(x = factor(COST), y = Percentage, fill = Vote)) +
  geom_bar(stat = "identity", position = "dodge") +  # Add position = "dodge" for side-by-side bars
  labs(
    title = "",
    x = "Bid Level",
    y = "Percentage (%)",
    fill = "Vote"
  ) +
  theme_minimal()+
  scale_fill_manual(
    values = c("0" = "lightblue", "1" = "maroon"),          # Assign colors
    labels = c("0" = "No Vote", "1" = "Yes Vote")   # Rename legend elements
  ) +
  theme(
    panel.grid = element_blank(),                   # Remove grid lines
    axis.line = element_line(size = 0.8, color = "black"),  # Add main axes
    axis.ticks = element_line(size = 0.8, color = "black"), # Add tick marks
    axis.ticks.length = unit(5, "pt"),              # Length of tick marks
    legend.position = "bottom",
    legend.title = element_blank()
  ) 

```

2.  **Vote count % at different bid levels in a summary table**

```{r,echo=FALSE,warning=FALSE, message=FALSE}

df_summary <- df1 %>%
  group_by(COST) %>%
  summarize(
    `Yes count` = sum(VOTE == 1),  # Count of votes equal to 1
    `No count` = sum(VOTE == 0),  # Count of votes equal to 0
    `Total Votes` = n(),         # Total number of votes
    `Yes (%)` = (`Yes count` / `Total Votes`) * 100,  # Percentage of votes equal to 1
    `No (%)` = (`No count` / `Total Votes`) * 100   # Percentage of votes equal to 0
  )

# Convert the dataframe to a flextable
#table <- flextable(df_summary)


kable(df_summary, caption = "Summary of vote counts", format = "html")


#print(table)

```

3a. **Percentage of Age Brackets Across Groups: Movies, Politics, and Environment**

```{r,echo=FALSE,warning=FALSE, message=FALSE}

df <- read_sav("~/Library/CloudStorage/OneDrive-UniversityofSaskatchewan/Chapter III-UseNonUseValue/R Project/Chapter-III/Rawdata//Water_Quality.sav 2")  # Adjusted filename

#df <- read_sav("./Rawdata/Water_Quality.sav 2")

df1 <- df%>%
  select(CaseId,AGE, GENDER, INCOME)%>%
  mutate(age = case_when(AGE ==1 ~ "18 to 24 years",
                         AGE ==2 ~ "25 to 29 years",
                         AGE ==3 ~ "30 to 34 year",
                         AGE ==4 ~ "35 to 39 years",
                         AGE ==5 ~ "40 to 44 years",
                         AGE ==6 ~ "45 to 49 years",
                         AGE ==7 ~ "50 to 54 years",
                         AGE ==8 ~ "55 to 59 years",
                         AGE ==9 ~ "60 to 64 years",
                         AGE ==10 ~ "65 to 69 years",
                         AGE ==11 ~ "70 to 74 years",
                         AGE ==12 ~ "75 to 79 years",
                         AGE ==13 ~ "80 to 84 years",
                         AGE ==14 ~ "85 years and older",
                         TRUE ~ NA_character_ ))%>%
  mutate(gender = case_when(GENDER ==1 ~ "Male",
                            GENDER ==2 ~ "Female",
                            GENDER ==3 ~ "Other",
                            TRUE ~ NA_character_ ))%>%
  mutate(income = case_when(INCOME ==0 ~ "Under $10,000",
                            INCOME ==1 ~ "$10,000 to $19,999",
                            INCOME ==2 ~ "$20,000 to $29,999",
                            INCOME ==3 ~ "$30,000 to $39,999",
                            INCOME ==4 ~ "$40,000 to $49,999",
                            INCOME ==5 ~ "$50,000 to $59,999",
                            INCOME ==6 ~ "$60,000 to $69,999",
                            INCOME ==7 ~ "$70,000 to $79,999",
                            INCOME ==8 ~ "$80,000 to $89,999",
                            INCOME ==9 ~ "$90,000 to $99,999",
                            INCOME ==10 ~ "$100,000 to $124,999",
                            INCOME ==11 ~ "$125,000 to $149,999",
                            INCOME ==12 ~ "$150,000 and over",
                            TRUE ~ NA_character_ 
                            
  ))


# Calculate percentages
age_percentages <- df1 %>%
  filter(!is.na(age)) %>%
  count(age) %>%
  mutate(percentage = n / sum(n) * 100)

ggplot(age_percentages, aes(x = factor(age), y = percentage)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),width = 0.5) +  # Dodge for side-by-side bars
  labs(x = "", y = "Percentage (%)", title = "") +
  scale_x_discrete(labels = c("1" = "Strongly agree", "2" = "Agree", "3" = "Unsure", "4" = "Disagree", "5" = "Strongly disagree")) +
  scale_fill_manual(values = c("Movies" = "darkblue", "Politics" = "maroon", "Environment" = "darkgreen")) +
  theme_minimal() +  # Apply theme_minimal() once
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    legend.text = element_text(size = 8),
    axis.text = element_text(size = 9),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_text(angle = 90, hjust = 1, size = 8),  # Rotate x-axis labels
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    plot.title = element_text(size = 8),
    legend.key.size = unit(0.2, "cm")  # Change the size of the legend marks (adjust the unit size as needed)
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 5),  # Set y-axis breaks
    labels = seq(0, 100, by = 5),  # Set y-axis labels
    limits = c(0, 25)  # Set y-axis limits (optional)
  )


```

3b. **Percentage of Gender Across Groups: Movies, Politics, and Environment**

```{r,echo=FALSE,warning=FALSE, message=FALSE}

# Calculate percentages = Movies - gender
gender <- df1 %>%
  filter(!is.na(gender)) %>%
  count(gender) %>%
  mutate(percentage = n / sum(n) * 100)



ggplot(gender, aes(x = factor(gender), y = percentage)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),width = 0.4) +  # Dodge for side-by-side bars
  labs(x = "", y = "Percentage (%)", title = "") +
  scale_x_discrete(labels = c("1" = "Strongly agree", "2" = "Agree", "3" = "Unsure", "4" = "Disagree", "5" = "Strongly disagree")) +
  scale_fill_manual(values = c("Movies" = "darkblue", "Politics" = "maroon", "Environment" = "darkgreen")) +
  theme_minimal() +  # Apply theme_minimal() once
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    legend.text = element_text(size = 8),
    axis.text = element_text(size = 9),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_text(hjust = 1, size = 8),  # Rotate x-axis labels
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    plot.title = element_text(size = 8),
    legend.key.size = unit(0.2, "cm")  # Change the size of the legend marks (adjust the unit size as needed)
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 70)  # Set y-axis limits (optional)
  )
```

3c. **Percentage of Income Brackets Across Groups: Movies, Politics, and Environment**

```{r,echo=FALSE,warning=FALSE, message=FALSE}

# Calculate percentages = Movies - Income
income <- df1%>%
  filter(!is.na(income)) %>%
  count(income) %>%
  mutate(percentage = n / sum(n) * 100)%>%
  mutate(type = "Movies")


# Define the desired order (replace with your actual categories)
desired_order <- c("Under $10,000",
"$10,000 to $19,999",
"$20,000 to $29,999",
"$30,000 to $39,999",
"$40,000 to $49,999",
"$50,000 to $59,999",
"$60,000 to $69,999",
"$70,000 to $79,999",
"$80,000 to $89,999",
"$90,000 to $99,999",
"$100,000 to $124,999",
"$125,000 to $149,999",
"$150,000 and over")  # Example; adjust to your data

# Convert 'income' to a factor with custom levels
income$income <- factor(income$income, levels = desired_order)

ggplot(income, aes(x = factor(income), y = percentage)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),width = 0.5) +  # Dodge for side-by-side bars
  labs(x = "", y = "Percentage (%)", title = "") +
  theme_minimal() +  # Apply theme_minimal() once
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    legend.text = element_text(size = 8),
    axis.text = element_text(size = 9),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_text(angle = 90, hjust = 1, size = 8),  # Rotate x-axis labels
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    plot.title = element_text(size = 8),
    legend.key.size = unit(0.2, "cm")  
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 5),  # Set y-axis breaks
    labels = seq(0, 100, by = 5),  # Set y-axis labels
    limits = c(0, 20)  # Set y-axis limits 
  )

```

4 ***Q12. Please think about why you voted the way you did for the proposals.***

Alternative Keys:

A1 -I voted as if my household would face the stated cost

A2 - I am certain that it I voted the same way I would if I were voting in a public election

A3 - I voted on each proposal without any consideration of the other proposals

A4 - I voted as if the policies would achieve the stated improvements in water quality

A5 - I voted as if the information collected in this survey will be used to inform policy makers

```{r,echo=FALSE,warning=FALSE, message=FALSE}

df3 <- df %>%
  select(Q12_WHY_VOTED_A1, Q12_WHY_VOTED_A2, Q12_WHY_VOTED_A3, Q12_WHY_VOTED_A4, Q12_WHY_VOTED_A5) %>%
  rename(A1=Q12_WHY_VOTED_A1,
         A2=Q12_WHY_VOTED_A2,
         A3=Q12_WHY_VOTED_A3,
         A4=Q12_WHY_VOTED_A4,
         A5=Q12_WHY_VOTED_A5)%>%
  mutate(across(everything(), as.character)) %>%
  gather(key = "column", value = "value", A1,A2,A3,A4,A5) %>%
  group_by(column, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(column) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()

# Make sure that NA is included in the factor levels
df3$value <- factor(df3$value, levels = c("1", "2", "3", "NA"))



# Create a bar plot based on the output with legend

ggplot(df3, aes(x = value, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "dodge",width = 0.3) +  # "dodge" for side-by-side bars
  facet_wrap(~ column,ncol = 5) +  # Facet by 'column' to create separate plots for each
  labs(
    title = "",
    y = "Percentage (%)",
    fill = "Response Value"  # Rename the legend here
  ) +
  scale_fill_manual(
    values = c("1" = "darkred", "2" = "yellow2", "3" = "green4", "NA" = "gray"),  # Customize colors
    labels = c("1" = "Disagree", "2" = "Neutral", "3" = "Agree", "NA" = "No Response")  # Rename the legend items
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    axis.text = element_text(size = 8),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    legend.key.size = unit(0.2, "cm")
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 60)  # Set y-axis limits (optional)
  )


```

4 ***Q13. When deciding whether to vote yes or no on the water quality proposals, how much did each of the policy features influence your votes?***

Alternative Keys:

A1: The cost of the policy in additional taxes

A2: The size of the region affected by the policy

A3: Whether the policy improved water quality near my home

A4: Improvements in the water quality level

```{r,echo=FALSE,warning=FALSE, message=FALSE}
df4 <- df %>%
  select(Q13_POLICY_INFLUENCE_A1,Q13_POLICY_INFLUENCE_A2,Q13_POLICY_INFLUENCE_A3,Q13_POLICY_INFLUENCE_A4) %>%
  rename(A1=Q13_POLICY_INFLUENCE_A1,
         A2=Q13_POLICY_INFLUENCE_A2,
         A3=Q13_POLICY_INFLUENCE_A3,
         A4=Q13_POLICY_INFLUENCE_A4)%>%
  mutate(across(everything(), as.character)) %>%
  gather(key = "column", value = "value", A1,A2,A3,A4) %>%
  group_by(column, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(column) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()

ggplot(df4, aes(x = value, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "dodge",width = 0.3) +  # "dodge" for side-by-side bars
  facet_wrap(~ column,ncol = 5) +  # Facet by 'column' to create separate plots for each
  labs(
    title = "",
    y = "Percentage (%)",
    fill = "Response Value"  # Rename the legend here
  ) +
  scale_fill_manual(
    values = c("1" = "darkred", "2" = "yellow2", "3" = "green4", "NA" = "gray"),  # Customize colors
    labels = c("1" = "Little or ni effect", "2" = "Moderate effect", "3" = "Large effect", "NA" = "No Response")  # Rename the legend items
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    axis.text = element_text(size = 8),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    legend.key.size = unit(0.2, "cm")
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 60)  # Set y-axis limits (optional)
  )



```

5.  ***Q14.How certain are you about your votes on the water quality proposals?***

```{r,echo=FALSE,warning=FALSE, message=FALSE}

df5 <- df %>%
  select(Q14_CERTAIN)%>%
  mutate(across(everything(), as.character)) %>%
  gather(key = "column", value = "value",Q14_CERTAIN) %>%
  group_by(column, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(column) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()


ggplot(df5, aes(x = value, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "dodge",width = 0.3) +  # "dodge" for side-by-side bars
  labs(
    title = "",
    y = "Percentage (%)",
    fill = "Response Value"  # Rename the legend here
  ) +
  scale_fill_manual(
    values = c("1" = "darkred", "2" = "yellow2", "3" = "green4", "4" = "blue4", "NA" = "gray"),  # Customize colors
    labels = c("1" = "Uncertain", "2" = "Somewhat Uncertain", "3" = "Somewhat certain","4"="Certain", "NA" = "No Response")  # Rename the legend items
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    axis.text = element_text(size = 8),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    legend.key.size = unit(0.2, "cm")
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 60)  # Set y-axis limits
  )

```

6.  ***Q15. To learn more about your general thoughts towards the water quality proposals you voted on, please select all statements that apply to you.***

Alternative Keys:

CH1 : I believe that new polices are important for well-being of people.

CH2 : I am not worried about water quality.

CH3 : I believe that new policies are important for the well-being of wildlife and plants.

CH4 : I did not read the information on the proposals carefully.

CH5 : I did not have enough information to make comfortable decisions

CH6 : I would like to see water quality improved, but I cannot afford to pay much for it

CH7 : I believe that my taxes are too high already and am against any initiative that will increase taxes

CH8 : I believe that funding a new water quality policy is well worth it to me

CH9 : It was difficult for me to decide how to vote

CH10 : Other (Please specify)

```{r,echo=FALSE,warning=FALSE, message=FALSE}
df6 <- df %>%
  select(Q15_GENERAL_THOUGHTSM1,Q15_GENERAL_THOUGHTSM2,Q15_GENERAL_THOUGHTSM3,Q15_GENERAL_THOUGHTSM4,
         Q15_GENERAL_THOUGHTSM5,Q15_GENERAL_THOUGHTSM6,Q15_GENERAL_THOUGHTSM7,Q15_GENERAL_THOUGHTSM8,
         Q15_GENERAL_THOUGHTSM9,Q15_GENERAL_THOUGHTSM10)%>%
  rename(CH1=Q15_GENERAL_THOUGHTSM1,
         CH2=Q15_GENERAL_THOUGHTSM2,
         CH3=Q15_GENERAL_THOUGHTSM3,
         CH4=Q15_GENERAL_THOUGHTSM4,
         CH5=Q15_GENERAL_THOUGHTSM5,
         CH6=Q15_GENERAL_THOUGHTSM6,
         CH7=Q15_GENERAL_THOUGHTSM7,
         CH8=Q15_GENERAL_THOUGHTSM8,
         CH9=Q15_GENERAL_THOUGHTSM9,
         CH10=Q15_GENERAL_THOUGHTSM10)%>%
  summarise(across(everything(), ~ sum(!is.na(.)), .names = "{col}"))%>%
  pivot_longer(
    cols = everything(),         # Select all columns to pivot
    names_to = "Column",         # Name for the column with original column names
    values_to = "NonNA_Count"    # Name for the column with counts
  )%>%
  mutate(Value = NonNA_Count/1297*100,
         )

df6 <- df6 %>%
  mutate(Column = factor(Column, levels = paste0("CH", 1:10)))  # Set levels explicitly

  
ggplot(df6, aes(x = Column, y = Value)) +
  geom_bar(stat = "identity", width = 0.4) +  # Use 'identity' to plot the actual values
  labs(
    title = "",
    x = "",
    y = "Percentage (%)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    legend.title = element_blank(),  # Remove the legend title if not needed
    axis.text = element_text(size = 8),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.line = element_line()  # Keep axis lines visible
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 100)  # Set y-axis limits (optional)
  )



```

7.  ***Q16. Thinking about this survey and what you read, did the survey push you to vote one way or another, or did it let you make up your mind about which way to vote on the various proposals?***

Alternative Keys:

Choice 1: The survey pushed me to vote against new water quality proposals

Choice 2: The survey let me make up my own mind

Choice 3: The survey pushed me to vote in favor of new water quality proposals

```{r,echo=FALSE,warning=FALSE, message=FALSE}
df7 <- df %>%
  select(Q16_SURVEY_VOTE_CHANGE)%>%
  mutate(across(everything(), as.character)) %>%
  gather(key = "column", value = "value",Q16_SURVEY_VOTE_CHANGE) %>%
  group_by(column, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(column) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()


ggplot(df7, aes(x = value, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "dodge",width = 0.3) +  # "dodge" for side-by-side bars
  labs(
    title = "",
    y = "Percentage (%)",
    fill = "Response Value"  # Rename the legend here
  ) +
  scale_fill_manual(
    values = c("1" = "maroon", "2" = "darkgreen", "3" = "darkblue", "NA" = "gray"),  # Customize colors
    labels = c("1" = "Choice 1", "2" = "Choice 2", "3" = "Choice 3","NA" = "No Response")  # Rename the legend items
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    axis.text = element_text(size = 12),  # Adjust axis text size
    axis.title = element_text(size = 14),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line()  # Keep axis lines visible
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 85)  # Set y-axis limits (optional)
  )



```

8 ***Q17. To what extent to you agree or disagree with the following statements.***

A1 : Humans have the right to modify the natural environment to suit their needs

A2 : Humans are severely abusing the planet

A3 : Plants and animals have the same right to exist as humans

A4 : Nature is strong enough to cope with the impacts of modern industrial nations

A5 : Humans were meant to rule over the rest of nature

A6 : The balance of nature is very delicate and easily upset

```{r,echo=FALSE,warning=FALSE, message=FALSE}
df8 <- df %>%
  select(SURVEY_CONTENT,Q17_A1_2,Q17_A2_2,Q17_A3_2,Q17_A4_2,Q17_A5_2,Q17_A6_2) %>%
  rename(A1=Q17_A1_2,
         A2=Q17_A2_2,
         A3=Q17_A3_2,
         A4=Q17_A4_2,
         A5=Q17_A5_2,
         A6=Q17_A6_2)%>%
  mutate(across(everything(), as.character)) %>%
  gather(key = "column", value = "value", A1,A2,A3,A4,A5, A6) %>%
  group_by(column, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(column) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()


# Make sure that NA is included in the factor levels
df8$value <- factor(df8$value, levels = c("1", "2", "3","4","5","6"))



# Create a bar plot based on the output with legend

ggplot(df8, aes(x = value, y = percentage, fill = value)) +
  geom_bar(stat = "identity", position = "dodge",width = 0.3) +  # "dodge" for side-by-side bars
  facet_wrap(~ column,ncol = 3) +  # Facet by 'column' to create separate plots for each
  labs(
    title = "",
    y = "Percentage (%)",
    fill = "Response Value"  # Rename the legend here
  ) +
  scale_fill_manual(
    values = c("1" = "maroon", "2" = "darkgreen", "3" = "darkblue","4"="yellow", "5"="purple4", "6" = "gray"),  # Customize colors
    labels = c("1" = "Strongly agree", "2" = "Agree", "3" = "Unsure", "4"= "Disagree", "5"="Strongly disagree ", "NA" = "No Response")  # Rename the legend items
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    legend.text = element_text(size = 8),
    axis.text = element_text(size = 8),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    legend.key.size = unit(0.2, "cm")  # Change the size of the legend marks (adjust the unit
  )+
  scale_y_continuous(
    breaks = seq(0, 100, by = 10),  # Set y-axis breaks
    labels = seq(0, 100, by = 10),  # Set y-axis labels
    limits = c(0, 60)  # Set y-axis limits (optional)
  )

```

9 How Q17 answers varied between groups of Environment, Movies and

***Q17. To what extent to you agree or disagree with the following statements.***

A1 : Humans have the right to modify the natural environment to suit their needs

A2 : Humans are severely abusing the planet

A3 : Plants and animals have the same right to exist as humans

A4 : Nature is strong enough to cope with the impacts of modern industrial nations

A5 : Humans were meant to rule over the rest of nature

A6 : The balance of nature is very delicate and easily upset

```{r,echo=FALSE,warning=FALSE, message=FALSE}

df8 <- df %>%
  select(SURVEY_CONTENT,Q17_A1_2,Q17_A2_2,Q17_A3_2,Q17_A4_2,Q17_A5_2,Q17_A6_2) %>%
  rename(A1=Q17_A1_2,
         A2=Q17_A2_2,
         A3=Q17_A3_2,
         A4=Q17_A4_2,
         A5=Q17_A5_2,
         A6=Q17_A6_2)



df8 <- df8%>%
  mutate(across(everything(), as.character)) %>%
  gather(key = "column", value = "value", A1,A2,A3,A4,A5,A6) %>%
  group_by(column, value) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(column) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()





df8_A <- df8%>%
  filter(column == "A1")%>%
  select(value,percentage)%>%
  rename("Movies" = "percentage")


df8 <- df8%>%
  left_join(df8_A )


# Create side-by-side bar plot
ggplot(df8, aes(x = factor(value), y = percentage, fill = column)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),width = 0.4) +  # Dodge for side-by-side bars
  labs(x = "", y = "Percentage", title = "A1 : Humans have the right to modify the natural environment to suit their needs") +
  scale_x_discrete(labels = c("1" = "Strongly agree", "2" = "Agree", "3" = "Unsure", "4" = "Disagree", "5" = "Strongly disagree")) +
  #scale_fill_manual(values = c("Movies" = "darkblue", "Politics" = "maroon", "Environment" = "darkgreen")) +
  theme_minimal() +  # Apply theme_minimal() once
  theme(
    legend.position = "bottom",  # Place the legend at the bottom
    legend.title = element_blank(),  # Remove the legend title if not needed
    legend.text = element_text(size = 8),
    axis.text = element_text(size = 8),  # Adjust axis text size
    axis.title = element_text(size = 8),  # Adjust axis title size
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.title.x = element_blank(),  # Remove the x-axis label
    axis.text.x = element_text(angle = 90, hjust = 1, size = 8),  # Rotate x-axis labels
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    axis.line = element_line(),  # Keep axis lines visible
    plot.title = element_text(size = 8),
    legend.key.size = unit(0.2, "cm")  # Change the size of the legend marks (adjust the unit size as needed)
  )

```

